Numerical trajectory patterns of floating macroalgae

### 2021-01-11 thesis_chapter_3.Rmd
chnages made to plots

```{r density plots, message=FALSE, warning=FALSE, echo=FALSE}

## Heatmaps of study domain, use previous data for study site map and histograms

@@

Max_ShapeFloat_H100_W00 <- tidync("OceanParcels/trajectory_data/Max_ShapeFloat_H100_W00.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, kelpvelU, kelpvelV) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
Max_ShapeFloat_H100_W00_mean <- Max_ShapeFloat_H100_W00 %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Max_ShapeFloat_H100_W00$type <- "Max_ShapeFloat_H100_W00" # add extra column 'type' to dataframe and assigned 'kelp' label

# Make mean trajectory plot
shape_plot <- ggplot()+
  geom_path(data = p_RK4_mean, aes(x = lon, y = lat), color = 'black')+
  geom_path(data = Max_Kfloat_H100_W00_mean, aes(x = lon, y = lat), color = 'blue')+
  geom_path(data = Max_ShapeFloat_H100_W00_mean, aes(x = lon, y = lat), color = 'orange')+
  xlab("Longtitude") + 
  ylab("Latitude") +
  ggtitle("Mean trajectory comparison") +
  #guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

# make density map
heatmap_Max_ShapeFloat_H100_W00 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Max_ShapeFloat_H100_W00, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "gradient", limits = c(1, 13000)) +
  geom_path(data = Max_Kfloat_H100_W00_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  ggtitle("Cylinder") + 
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

# make another density map for the maximum so that title can be manipulated

heatmap_Max_Sphere_H100_W00 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Max_Kfloat_H100_W00, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "gradient", limits = c(1, 13000)) +
  geom_path(data = Max_Kfloat_H100_W00_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("Sphere") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

shape_data_total <- rbind(Max_Kfloat_H100_W00, Max_ShapeFloat_H100_W00)

@@

ggarrange(shape_plot, shape_dis_plot, heatmap_Max_Sphere_H100_W00, heatmap_Max_ShapeFloat_H100_W00, labels = c("AUTO"), common.legend = TRUE, legend = c("bottom"), ncol = 2, nrow = 2)

>>>>

```{r density plots, message=FALSE, warning=FALSE, echo=FALSE}
## Heatmaps of study domain, use previous data for study site map and histograms

@@

sphere <- tidync("OceanParcels/trajectory_data/Max_KFloat_H100_W00.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, kelpvelU, kelpvelV) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
sphere_mean <- sphere %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

sphere$type <- "Sphere" # add extra column 'type' to dataframe and assigned 'kelp' label
sphere_mean$type <- "Sphere" # add extra column 'type' to dataframe and assigned 'kelp' label

# read in data again for one max simulation, as cannot sort issue out with rename df...
cyl <- tidync("OceanParcels/trajectory_data/Max_ShapeFloat_H100_W00.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, kelpvelU, kelpvelV) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
cyl_mean <- cyl %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

cyl$type <- "Cylinder" # add extra column 'type' to dataframe and assigned 'kelp' label
cyl_mean$type <- "Cylinder" # add extra column 'type' to dataframe and assigned 'kelp' label

# Make mean trajectory plot
shape_plot <- ggplot()+
  geom_path(data = p_RK4_mean, aes(x = lon, y = lat), color = 'black')+
  geom_path(data = sphere_mean, aes(x = lon, y = lat), color = 'blue')+
  geom_path(data = cyl_mean, aes(x = lon, y = lat), color = 'orange')+
  xlab("Longtitude") + 
  ylab("Latitude") +
  ggtitle("Mean trajectory comparison") +
  #guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

# make density map
heatmap_sphere <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = sphere, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "gradient", limits = c(1, 13000)) +
  geom_path(data = sphere_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  ggtitle("Cylinder") + 
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_cyl <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = cyl, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "gradient", limits = c(1, 13000)) +
  geom_path(data = cyl_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("Sphere") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

shape_data_total <- rbind(sphere, cyl)

@@

ggarrange(shape_plot, shape_dis_plot, heatmap_sphere, heatmap_cyl, labels = c("AUTO"), common.legend = TRUE, legend = c("bottom"), ncol = 2, nrow = 2)
